---
title: "Generating observations from epidemic simulations"
author: "Lucy M Li"
date: "3/16/2017"
output: pdf_document
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(grid)
library(gridExtra)
source("../R/simulations.R")
source("../R/simulate_data.R")
source("../R/visualize.R")
```

## Epidemic simulations using the SIR model

The Susceptible-Infected-Removed (SIR) is a simple state-space-model in which infected individuals $I(t)$ cause infections in susceptible individuals $S(t)$ at a rate $\beta \frac{I}{N}$. Infected individuals are removed (through recovery or death) at a rate $\gamma$. The duration of infection is $D = 1\frac{1}{\gamma}$ and the basic reproduction number is $R_0 = \beta D$.


```{r SIRsimulations}
set.seed(20170317)
simulated.epidemic <- SIR(beta=0.15, gamma=1/10, 
                          init.states=list(S=1000, I=1, R=0), 
                          time.step=0.25, num.steps=800, 
                          agg.time.steps=4) # aggregate incidence reports temporally
simulated.data <- get_SIR_data(simulated.epidemic, reporting=0.25, filename="../data/sim_SIR_beta_0.15_gamma_0.1_rho_0.25.csv") # 25% sampling probability
```


```{r SIRsimulationsPlots, fig.width=6, fig.height=5}
simulation.plot <- visualize.SIR(simulated.data)
grid.draw(simulation.plot)
```

